---
title: "Collateralized Loan Obligation"
output: html_notebook
---

## Learning objective

This notebook mirrors the public Python CLO example in R. It keeps the chapter
small and focused:

- calibrate a one-factor asset correlation from repeated cohort default-rate dispersion
- hold marginals fixed and compare a low-rho and high-rho regime
- map collateral loss into true tranche-by-tranche principal loss
- report pathwise warning-trigger frequencies and loss-compensation spreads

## The waterfall map

For a tranche with attachment $a$ and detachment $b$, principal loss on
collateral par is

$$
\ell_{[a,b]}(L_f)=\min\{\max(L_f-a,0),\,b-a\}.
$$

As a fraction of tranche notional,

$$
\tilde{\ell}_{[a,b]}(L_f)=\frac{\ell_{[a,b]}(L_f)}{b-a}.
$$

## Dependence calibration

The public implementation estimates $\rho$ from repeated cohort default-rate
dispersion. Let cohort $j$ have default rate $r_j=d_j/n_j$. The fitted
one-year PD is

$$
p=\frac{\sum_j d_j}{\sum_j n_j},
$$

and the Vasicek pairwise joint-default probability is

$$
q_2(\rho)=\Phi_2\bigl(\Phi^{-1}(p),\,\Phi^{-1}(p);\,\rho\bigr).
$$

The calibration chooses the $\rho$ that best matches the observed
cross-cohort variance of $r_j$.

```{r}
source("CLO.R", local = globalenv())
```

## Scenario table

```{r}
scenario_table
```

## Tranche summary

```{r}
summary_table
```

## Rendered outputs

The sample figures and tables written by this notebook live in
`rendered-sample/`.
